\documentclass[margin,line]{resume}
\usepackage{hyperref}

\begin{document}

\name{\Large Shaifali Agrawal's \Resume}

\begin{resume}

    % Contact Information    
    \section{\mysidestyle Contact\\Information}\vspace{2mm}
    \begin{tabular}{@{} l @{\hspace{69mm}} r}
    agrawalshaifali09@gmail.com & \url{http://exploreshaifali.github.io}\\+91-7509119894	 \\
    \end{tabular}

    % Academic/Research Interests
    \section{\mysidestyle Interests}

    Cloud Platform (OpenStack, AWS), Full Stack Web Dev (Python, Django, Bootstrap), Database (PostgreSQL, MongoDB), Data Science, Unix-like (Ubuntu).

    % Professional Experience
    \section{\mysidestyle Employment\\Activies}

    \begin{list2}
    
    \item \textbf{Backend Lead at Hashgrowth} \hspace{69mm} Oct 2016 onwards \\ Python/Django, backend engineer to develop an App Store Optimization Platform.
    
    \item \textbf{Software Developer at Zaya Learning Labs} \hspace{45mm} Jan - Oct 2016 \\ Python/Django, Django Rest Framework backend engineer to develop distributed web app for Zaya Learning Labs.\url{http://zaya.in/}
    
	\item \textbf{Google Summer of Code 2015 Intern (Systers, Anita Brog Institute)} \hspace{1mm} May- August 2015 \\ Full Stack Python/Django, Bootstrap, PostgreSQL web development to build meetup management application that facilitate Systers Portal. \url{http://portal.systers.org/}

	\item \textbf{Outreachy(OPW) round 9 Intern (OpenStack Foundation)} \hspace{18mm} Dec 2014 - March 2015 \\ Splitting the data and control planes of Zaqar's(messaging service of OpenStack) storage layer.

	\item \textbf{Developer (Development Center, IIPS)} \hspace{52mm} Oct 2012 - Sept 2014 \\ Volunteer developer at e-governance center at IIPS, Devi Ahilya University.

	\end{list2}

    % Skills
    \section{\mysidestyle Skills} 

    \begin{list2}
	\item \textbf{Programming/Scripting}: \hspace{3mm} Python, Java(J2SE), Javascript, bash
	\item \textbf{Web Development}: \hspace{13mm}  Django, Django Rest Framework, Bootstrap, HTML, CSS
	\item \textbf{Databases}: \hspace{28mm} PostgreSQL, MySQL, SQLite,	MongoDB
	\item \textbf{Cloud and Virtualization}: \hspace{1mm} OpenStack, AWS, Docker,  DigitalOcean
	\item \textbf{Operating Systems}: \hspace{12mm} *nix, Windows
    \item \textbf{Version Control Systems}: \hspace{2mm} Git
	\end{list2}

    % Talks
    \section{\mysidestyle Talks}
    \begin{list2}
    \item \textbf{Getting Started with python-openstacksdk } (at OpenStack Summit, 27-Oct 2016)\url{https://www.youtube.com/watch?v=VE3PjUMy8aw}
    \end{list2}

    \begin{list2}
    \item \textbf{Outreachy with OpenStack Zaqar} (at OpenStack Day India 2015, 8-Aug 2015)\url{http://tinyurl.com/nomuog6}
    \end{list2}

    \begin{list2}
    \item \textbf{OpenStack Components} (at OpenStack meetup in Indore, 19-Dec 2015)\url{http://tinyurl.com/gscb7cd}
    \end{list2}

    % Education \\ *- ONGOING
    \section{\mysidestyle Education}

    \begin{list2}
	\item \textbf{Master of Computer Applications} \hspace{70mm} \textbf{CGPA: 8.91/10} \\ International Institute of Professional Studies, Devi Ahilya University \hspace{17mm} July 2013 - April 2016
	\end{list2}

	\begin{list2}
	\item \textbf{Bachelor of Computer Applications} \hspace{70mm} \textbf{CGPA: 9.07/10} \\ International Institute of Professional Studies, Devi Ahilya University \hspace{20mm} July 2010 - May 2013
	\end{list2}

    % Projects
    \section{\mysidestyle Projects} 
	\begin{list2}

    \item \textbf{Django-SoftDelete-It}: A django app to implement soft-delete functionality in desired model.\url{https://github.com/exploreshaifali/django-softdelete-it}
    \item \textbf{Splitting Data and Control Planes}: Round 9 Outreachy(OPW) internship project; To separate the two planes of Storage layer of OpenStack's Zaqar component.\url{http://tinyurl.com/plkb3zv}
    \item \textbf{AWS S3 Video Compress}: Full Stack Python/Django, AWS S3, Celery, Redis, PostgreSQL, ffmpeg, Bootstrap web development; Upload video on AWS S3, compress video through ffmpeg and Celery queues, tasks; store compressed video back on S3. \url{http://bit.ly/github-aws-s3-video-compress}
    \item \textbf{Meetup management app}: Google Summer of Code 2015 project; Full Stack Python/Django, Bootstrap, PostgreSQL web development to build meetup management application that facilitate Systers Portal. \url{http://portal.systers.org/}	
    \item \textbf{Help The Needy!}: Women's Day hackathon; NGO locator based on users location. Python/Django, Bootstrap \url{http://bit.ly/help-the-needy-code}
	\item \textbf{Automation of Bonafied Certificate System}: Desktop Application, developed using Java,
    SQLite, Netbeans, Jasper Reporter, aimed to automate the creation of Bonafied certificate in IIPS, DAVV. \url{https://github.com/exploreshaifali/bonafidePro}
    \end{list2}

    % Certifications \\ *- ONGOING
    \section{\mysidestyle Online \\ Courses}

    \begin{list2}
	\item \textbf{Statistical Learning} (Standford OpenedX)
	\item \textbf{6001:Introduction to Computer Science and Programming with Python} (edX)
	\item \textbf{Computing for Data Analysis} (Coursera)
	\end{list2}

    % Miscellaneous
    \section{\mysidestyle Other \\ Information}
    \begin{list2}
    \item Hobbies: Dance, Arts and Craft, Blogging
    \item Languages: English, Hindi
    \item Citizenship: India
    \item Relocation preference: Willing to relocate to a new city/country or work remotely.   
    \end{list2}
    % References
    \section{\mysidestyle References} 

    \begin{list2}
    \item {\sl Shaligram Prajapat} (Associate Professor, International Institute of Professional Studies, Devi Ahilya University), shaligram.prajapat@gmail.com
    \end{list2}

\end{resume}
\end{document}